opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-12-08 chapters/03_existing_datasets.tex
Added paragraphs on data correlation and filtering mechanisms

\begin{table}[!htb]
\centering
\caption{Overview of Experimental Powder Diffraction Databases}
\label{tab:exp_databases}
\scalebox{0.85}{
\begin{tabular}{@{}cccccccc@{}}
\toprule
\textbf{Name} & \textbf{No. of Patterns} & \textbf{O.A.} & \textbf{Comp.} & \textbf{Spg} & \textbf{Lattice} & \textbf{Unit Cell} & \textbf{Year est.} \\
\midrule
Linus Pauling file                     & 21,700                    & \xmark          & \cmark        & \cmark        & \cmark        & \cmark          & 2002            \\
Powder Diffraction File \tablefootnote{The PDF lists the Material Platform for Data Science (MPDS) as a database source. Since the MPDS is hosted by the Pauling File project, there is likely significant overlap in the experimental patterns available in the PDF and the Linus Pauling File.} & 20,800 & \xmark & \cmark & \cmark & \cmark & \cmark & 1941 \\
RRUFF                                  & 1290                      & \cmark          & \cmark        & \cmark        & \cmark        & \xmark          & 2006            \\
Crystallography Open Database          & 1063                      & \cmark          & \cmark        & \cmark        & \cmark        & \cmark          & 2003            \\
PowBase                                & 169                       & \cmark          & \xmark        & \xmark        & \xmark        & \xmark          & 1999            \\
\bottomrule
\end{tabular}}
\end{table}

@@

\textbf{Crystallography Open Database:} \cite{CODWeb} The Crystallography Open Database (COD) is an open-access collection of crystal structures founded in 2003\cite{Graulis2009cod}. It currently provides over 500,000 crystal structures. Of these files, 1063 contain the experimental powder diffraction data that was used to determine the underlying crystal structures of the investigated samples. Hence, the experimental powder diffraction data contained in the COD is labeled with the full crystal structure information. \\

>>>>

\begin{table}[!htb]
\centering
\caption{Overview of Experimental Powder Diffraction Databases}
\label{tab:exp_databases}
\scalebox{0.85}{
\begin{tabular}{@{}cccccccc@{}}
\toprule
\textbf{Name} & \textbf{No. of Patterns} & \textbf{O.A.} & \textbf{Comp.} & \textbf{Spg} & \textbf{Lattice} & \textbf{Unit Cell} & \textbf{Year est.} \\
\midrule
Linus Pauling file                     & 21,700                    & \xmark          & \cmark        & \cmark        & \cmark        & \cmark          & 2002            \\
Powder Diffraction File \tablefootnote{The PDF lists the Material Platform for Data Science (MPDS) as a database source. Since the MPDS is hosted by the Pauling File project, there is likely significant overlap in the experimental patterns available in the PDF and the Linus Pauling File.} & 20,800 & \xmark & \cmark & \cmark & \cmark & \cmark & 1941 \\
RRUFF                                  & 1290                      & \cmark          & \cmark        & \cmark        & \cmark        & \xmark          & 2006            \\
Crystallography Open Database          & 1052                      & \cmark          & \cmark        & \cmark        & \cmark        & \cmark          & 2003            \\
PowBase                                & 169                       & \cmark          & \xmark        & \xmark        & \xmark        & \xmark          & 1999            \\
\bottomrule
\end{tabular}}
\end{table}

@@

\textbf{Crystallography Open Database:} \cite{CODWeb} The Crystallography Open Database (COD) is an open-access collection of crystal structures founded in 2003\cite{Graulis2009cod}. It currently provides over 500,000 crystal structures. Of these files, 1052 contain the experimental powder diffraction data that was used to determine the underlying crystal structures of the investigated samples. Hence, the experimental powder diffraction data contained in the COD is mostly labeled with the full crystal structure information. \\

### 2024-12-08 chapters/04_our_dataset.tex
Added paragraphs on data correlation and filtering mechanisms

In collaboration with several other institutions we have collected a dataset of diffractograms stemming from experiments, some of them labeled with corresponding structural information. The following paragraphs detail the contribution of each research group. Most data was collected using \ce{Cu} radiaton sources which have a  $K_{\alpha1}$ wavelength of $\lambda=1.54056\text{\AA}$ and a $K_{\alpha2}$ wavelength of $\lambda=1.54439\text{\AA}$.

\newcommand{\partialcheck}[1]{\textcolor{orange}{\ding{52}(#1\%)}}

\begin{table}[!htb]
\centering
\caption{opXRD database entries}
\label{tab:merged}
\scalebox{0.90}{
\begin{tabular}{@{}lllllll@{}}
\toprule
Institution & No. Patterns & Comp. & Spg & Lattice & Atom coords. & Research Project \\ 
\midrule
CNRS        & \qquad 1052          & \cmark   & \partialcheck{85}   & \cmark   &  \partialcheck{85}   & Extracted from the COD \\ 
HKUST(GZ)   & \qquad 21           & \cmark   & \cmark   & \cmark   & \cmark   & Phase identification reference database \\ 
USC         & \qquad 338          & \cmark   & \cmark   & \partialcheck{90}   & \xmark   & Study of CuNi and CuAl alloys          \\ 
EMPA        & \qquad 790          & \cmark   & \partialcheck{63}   & \xmark   & \xmark   & Tin halide perovskites, Zn-V-N library \\ 
INT         & \qquad 19,780        & \xmark   & \xmark   & \xmark   & \xmark   & Compilation of various projects        \\ 
IKFT        & \qquad 64           & \xmark   & \xmark   & \xmark   & \xmark   & Commercial catalysts, bulk materials   \\ 
LBNL        & \qquad n/a          & \xmark   & \xmark   & \xmark   & \xmark   & Time series recordings of Perovskites  \\ 
\bottomrule
\end{tabular}}
\end{table}

@@

%TODO: A paragraph on how data is correlated

>>>>

In collaboration with several other institutions we have collected a dataset of diffractograms stemming from experiments, some of them labeled with corresponding structural information. The following paragraphs detail the contribution of each research group. Most data was collected using \ce{Cu} radiaton sources which have a  $K_{\alpha1}$ wavelength of $\lambda=1.54056\text{\AA}$ and a $K_{\alpha2}$ wavelength of $\lambda=1.54439\text{\AA}$. We filtered the submitted datasets to exclude patterns with invalid features such as patterns with only one unique recorded angle, patterns in which all intensities were zero, or patterns that contained less than 50 recorded angles. \\

The below table Tab.$\eqref{tab:merged}$ provides an overview of the opXRD database. The columns to the right of No. patterns indicate the availability of properties of the underlying samples. The column titled ``Comp.'' indicates the availability of the chemical composition, and the column titled ``Spg'' indicates the availability of the spacegroup. The ``Lattice'' and ``Atom coords.'' columns indicate the availability of lattice parameters and atomic coordinates respectively.\\

\begin{table}[!htb]
\centering
\caption{The opXRD database}
\label{tab:merged}
\scalebox{0.9}{
\begin{adjustbox}{center}
\begin{tabular}{@{}lllllll@{}}
\toprule
Institution & No. patterns & Comp. & Spg. & Lattice & Atom coords. & Research Project \\ 
\midrule
CNRS        &  1052          & \cmark   & \partialcheck{85}   & \cmark   &  \partialcheck{85}   & Extracted from the COD \\ 
HKUST(GZ)   &  21           & \cmark   & \cmark   & \cmark   & \cmark   & Phase identification reference database \\ 
USC         &  338          & \cmark   & \cmark   & \partialcheck{90}   & \xmark   & Study of CuNi and CuAl alloys          \\ 
EMPA        &  790          & \cmark   & \partialcheck{63}   & \xmark   & \xmark   & Tin halide perovskites, Zn-V-N library \\ 
INT         &  19,780        & \xmark   & \xmark   & \xmark   & \xmark   & Compilation of various projects        \\ 
IKFT        &  64           & \xmark   & \xmark   & \xmark   & \xmark   & Commercial catalysts, bulk materials   \\ 
LBNL        &  n/a          & \xmark   & \xmark   & \xmark   & \xmark   & Time series recordings of Perovskites  \\ 
\bottomrule
\end{tabular}
\end{adjustbox}}
\end{table}

%TODO: A paragraph on how data is correlated
The degree of variation between the patterns is different for each contribution. For example, the CRNS and the INT contributions each are collections that encompass many research projects over a large period of time and hence exhibit a high degree of variability between individual patterns. In contrast, the contributions by the USC and the LBNL contain many very similar patterns. The patterns in the USC datasets are similar because the underlying samples are all variations of CuNi and CuAl alloys collected on the same machine. The LBNL patterns are similar because they stem from in-situ recordings where several hundred or several thousand patterns were collected over time per sample while they were undergoing physical processes. The following paragraphs describe each contribution individually. \\

@@
